Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-11-27 Journal1/paper1TNSM/pr.tex
add a bit code

In this paper, we study the problem of service aware baseband resource allocation and virtual network function (VNF) activation in O-RAN system using network slicing to isolate different types of services.

@@

Nevertheless, we break it down into two different steps where an iterative algorithm finds near optimal solution.

@@

The proposed method is validated via simulations which illustrate a higher data rate and lower end-to-end delay compared to existing methods. 

>>>>

In this paper, we study the problem of service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems using network slicing to isolate different types of services.

@@

Nevertheless, we break it down into two different steps where an iterative algorithm finds a near-optimal solution.

@@

The proposed method is validated via simulations that illustrate a higher data rate and lower end-to-end delay than existing methods. 
